# Replicating game: Colantone et al. (2024, APSR)

“The Political Consequences of Green Policies”

Authors: ...


## Background and goals

We are 'robustness replicating' Colantone et al (add reference here) for a replication game (see [Institute for replication](i4rep.org)


Main goals

1. Computationally reproduce key results (Do they computationally hold up, especially the 'main claims')

2. Robustness checks: Consider alternate plausible specifications and approaches; do the results persist?

3. Methodological (if time permits): critique methodology, provide further analysis (e.g., multiple hypothesis testing corrections, equivalence tests




## IGNORE CONTENT BELOW


:::{.callout-note collapse="true"}

## Expand To Learn About Collapse

This is an example of a 'folded' caution callout that can be expanded by the user. You can use `collapse="true"` to collapse it by default or `collapse="false"` to make a collapsible callout that is expanded by default.
:::


## Create an object to see if it crosses chapters

```{r create-xtest}


xtest <- 24

```


## Example of inline code

Before we defined the object `xtest` (see previous code block). You can also use integrate short code blocks into the narrative using "inline code" ... Type ``r xtest`` and the *value* of the object `xtest` shows up in your code, here `r xtest`.




## Showing some material

What if I want the code to be folded but not to spit results and side effects  onto the screen?

```{r}
#| results: false
#| label: hideresults

3+5

a <- "happiness"

```

`r a`

Did it display the sum?  Was the object defined?


## Labeling/captioning chunks

Wait, why do we just have 'code' labeling the chunks when you fold them. It would be much more useful to have a descriptive label you can see in the html. We can do this in each chunk with `#| code-summary: "blah blah"`, as below


Note: the chunk options content itself is not shown. Below, we have:

```
#| label: car-talk
#| code-summary: "Car talk stuff"

head(mtcars)

```


```{r}
#| label: car-talk
#| code-fold: true
#| code-summary: "Car talk stuff"

head(mtcars)

```
