# Overview and approach 

## Key details

"The Political Consequences of Green Policies"

Authors: ...

*Note:* the 'writeup' will be given in the chapter "[A comment on Colantone et al. (2024, APSR)](#writeup)

## Background and goals

We are 'robustness replicating' @colantone2024political (also noting @colantone2024political_cor) for a replication game (see [Institute for replication](i4rep.org)

Main goals

1.  Computationally reproduce key results (do they computationally hold up, especially the 'main claims'). See ['Computational replication'](#computational).

2.  Robustness checks: Consider alternate plausible specifications and approaches; do the results persist? See ['Robustness checks'](#robustness)

3.  Methodological (if time permits): critique methodology, provide further analysis (e.g., multiple hypothesis testing corrections, equivalence tests)

## The paper's main claim, evidence

###  **Main claim:**

 \~\'This policy caused people \[who were financially hurt\] to vote for Lega\'. \[or more generally to be more right wing\]

Background: \"The policy identifies the most polluting categories of vehicles and bans them from accessing and circulating within the area.\" 

### **Main evidence for this claim:** 

> the difference in the differences of outcomes by emission category, that is, between Diesel versus Petrol owners of Euro4, and Diesel versus Petrol owners of Euro5.\"

(Note it's a difference in differences without a time dimension, although they later consider vote switches) 


> Our main dependent variable is an indicator that takes the value 1 if the respondent reports voting for Lega, and 0 otherwise.

> the average estimated effect is 13.5 percentage points ... the baseline rate of support for Lega in the sample was 24.4%. ... owning a car affected by the vehicle ban raised the probability of voting for Lega in the subsequent elections by 55% above the baseline rate\"

### **Secondary claim(s)/other key claims:** 

> electoral change did not stem from a broader shift against environmentalism, but rather from disaffection with the policy\'s uneven pocketbook implications

They also, \~'people who were *compensated* did *not* shift in response to the policy'

These are implicitly claims of (1) null or bounded effects and (2) *differential* effects (for those compensated vs. those not compensated.) This is important to the authors' theoretical interpretation of the effect, and its generalization to political behavior as a whole.

## IGNORE CONTENT BELOW

::: {.callout-note collapse="true"}
## Expand To Learn About Collapse

This is an example of a 'folded' caution callout that can be expanded by the user. You can use `collapse="true"` to collapse it by default or `collapse="false"` to make a collapsible callout that is expanded by default.
:::

## Create an object to see if it crosses chapters

```{r create-xtest}


xtest <- 24

```

## Example of inline code

Before we defined the object `xtest` (see previous code block). You can also use integrate short code blocks into the narrative using "inline code" ... Type `r xtest` and the *value* of the object `xtest` shows up in your code, here `r xtest`.

## Showing some material

What if I want the code to be folded but not to spit results and side effects onto the screen?

```{r}
#| results: false
#| label: hideresults

3+5

a <- "happiness"

```

`r a`

Did it display the sum? Was the object defined?

## Labeling/captioning chunks

Wait, why do we just have 'code' labeling the chunks when you fold them. It would be much more useful to have a descriptive label you can see in the html. We can do this in each chunk with `#| code-summary: "blah blah"`, as below

Note: the chunk options content itself is not shown. Below, we have:

```         
#| label: car-talk
#| code-summary: "Car talk stuff"

head(mtcars)
```

```{r}
#| label: car-talk
#| code-fold: true
#| code-summary: "Car talk stuff"

head(mtcars)

```
